### 2023-11-14 manuscript/supplementary_methods.Rmd
fix instrument name in supplementary methods

FIE-HRMS mass spectra were acquired on on a Q-Exactive Orbitrap (ThermoFinnigan, San Jose CA) coupled to a Dionex (ThermoFinnigan, San Jose CA) ultra-performance LC system system for the *B. distachyon* samples and the Human urine. 
A sample volume of 20 $\mu$L was injected and delivered to the electrospray ionisation (ESI) source via a 'plug' flow solvent of pre-mixed HPLC grade MeOH (Fisher Scientific) and ultra-pure H~2~O (18.2 $\Omega$) at a ratio of 7:3. 
The initial flow rate was 60 $\mu$L min^-1^ for 0.4 minutes and increased to 200 $\mu$L min^-1^ over 0.8 minutes. 
The flow rate was maintained at 200 $\mu$L min^-1^ for 0.3 minutes then increased to 600 $\mu$L min^-1^ over 1.5 minutes. 
Then the flow rate was then returned to 60 $\mu$L min^-1^ for 0.5 minutes. 
The total gradient time was 3.5 minutes. The capillary temperature and voltage were set at 270 ^$\circ$^C and 37.50 kV respectively.

@@

C18-UHPLC-HRMS analyses were performed on an Orbitrap Fusion Tribrid mass spectrometer (Thermo Scientific) that was coupled to a Ultimate 3000 liquid chromatography tower (Dionex, Thermo Scientific). 
Mass spectra were acquired using a single scan filter for each of the positive and negative ionisation modes between a range of 100-2000 m/z. For all scan events, the scan rate was 1 Hz with a mass resolution of 100,000. The automatic gain control (AGC) target was 5 x10^5.

>>>>

FIE-HRMS mass spectra were acquired on on a Thermo Q-Exactive Plus Orbitrap (ThermoFinnigan, San Jose CA) coupled to a Dionex (ThermoFinnigan, San Jose CA) ultra-performance LC system system for the *B. distachyon* samples and the Human urine. 
A sample volume of 20 $\mu$L was injected and delivered to the electrospray ionisation (ESI) source via a 'plug' flow solvent of pre-mixed HPLC grade MeOH (Fisher Scientific) and ultra-pure H~2~O (18.2 $\Omega$) at a ratio of 7:3. 
The initial flow rate was 60 $\mu$L min^-1^ for 0.4 minutes and increased to 200 $\mu$L min^-1^ over 0.8 minutes. 
The flow rate was maintained at 200 $\mu$L min^-1^ for 0.3 minutes then increased to 600 $\mu$L min^-1^ over 1.5 minutes. 
Then the flow rate was then returned to 60 $\mu$L min^-1^ for 0.5 minutes. 
The total gradient time was 3.5 minutes. The capillary temperature and voltage were set at 270 ^$\circ$^C and 37.50 kV respectively.

@@

C18-UHPLC-HRMS analyses were performed on an Thermo Orbitrap Fusion Tribrid mass spectrometer (Thermo Scientific) that was coupled to a Ultimate 3000 liquid chromatography tower (Dionex, Thermo Scientific). 
Mass spectra were acquired using a single scan filter for each of the positive and negative ionisation modes between a range of 100-2000 m/z. For all scan events, the scan rate was 1 Hz with a mass resolution of 100,000. The automatic gain control (AGC) target was 5 x10^5.
